%% Roham Koohestani — Academic CV
%% Style inspired by Kathryn T. Stolee (ktstolee.github.io)
%% Compile: pdflatex cv.tex  (or use compile.sh)

\documentclass[11pt,letterpaper]{article}

\usepackage[top=0.85in,bottom=0.85in,left=1in,right=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{enumitem}

% ── Hyperlinks ────────────────────────────────────────────────────────────────
\hypersetup{
  colorlinks = true,
  urlcolor   = [rgb]{0.10,0.40,0.70},
  linkcolor  = [rgb]{0.10,0.40,0.70},
}

% ── Page style ────────────────────────────────────────────────────────────────
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\small Roham Koohestani}
\fancyfoot[C]{\small \today}
\fancyfoot[R]{\small \thepage\ of \pageref{LastPage}}

% ── Layout ────────────────────────────────────────────────────────────────────
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist{noitemsep, topsep=2pt, leftmargin=*}

% ── Section heading ───────────────────────────────────────────────────────────
\newcommand{\cvsection}[1]{%
  \vspace{14pt}%
  {\large\textbf{#1}}\\[-5pt]%
  \rule{\linewidth}{0.4pt}%
  \vspace{4pt}%
}

% ── Two-column entry (used for employment / education) ────────────────────────
%    \cvrow{left content}{right content}
\newcommand{\cvrow}[2]{%
  \begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
    #1 & #2
  \end{tabular*}%
}

% ── Publication entry  ────────────────────────────────────────────────────────
%    \pub{tag}{authors}{title}{venue}{links}
\newenvironment{publist}[1][0]{%
  \begin{list}{}{%
    \setlength{\leftmargin}{2.4em}%
    \setlength{\itemsep}{6pt}%
    \setlength{\parsep}{0pt}%
    \setlength{\topsep}{4pt}%
  }%
}{\end{list}}


% =============================================================================
\begin{document}

% ── Header ───────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\textbf{Roham Koohestani}}
\end{center}
\vspace{2pt}
\begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
  Researcher, JetBrains Research (HAX Team)
    & \href{mailto:roham.koohestani@jetbrains.com}{roham.koohestani@jetbrains.com} \\
  AISE Lab, Delft University of Technology
    & \href{https://rohamkoohestani.com}{rohamkoohestani.com} \\
  The Hague, Netherlands
    & \href{https://scholar.google.com/citations?user=xDkfR7UAAAAJ\&hl=en}{Google Scholar}
      \,/\, \href{https://orcid.org/0009-0000-1649-9596}{ORCID}
      \,/\, \href{https://github.com/RebelOfDeath}{GitHub} \\
\end{tabular*}
\vspace{4pt}
\hrule

% ── Research Interests ───────────────────────────────────────────────────────
\cvsection{Research Interests}
AI for software engineering: large language models for code, developer--AI interaction,
and the verification of agentic systems.
My aim is AI assistance that developers can trust, grounded in empirical evidence of
what they need and in formal guarantees designed to serve those needs.

% ── Employment ───────────────────────────────────────────────────────────────
\cvsection{Employment}

\cvrow{%
  \textbf{JetBrains Research} \hspace{4pt} The Hague, Netherlands%
}{2026 -- present}\\[1pt]
\hspace*{12pt} Researcher, Human-AI Experience (HAX) team.
Developer-centric trustworthy AI for software engineering.

\vspace{8pt}
\cvrow{%
  \textbf{JetBrains Research} \hspace{4pt} Amsterdam, Netherlands%
}{2025 -- 2026}\\[1pt]
\hspace*{12pt} Research Intern, Human-AI Experience team.
In-IDE calibration of LLMs at production scale (JetBrains--TU Delft AI4SE collaboration).

\vspace{8pt}
\cvrow{%
  \textbf{AISE Lab, Delft University of Technology} \hspace{4pt} Delft, Netherlands%
}{2024 -- present}\\[1pt]
\hspace*{12pt} Research Assistant, supervised by Prof.\ Maliheh Izadi.
Benchmarking, agent verification, and IDE personalization.

\vspace{8pt}
\cvrow{%
  \textbf{Syntho B.V.} \hspace{4pt} Amsterdam, Netherlands%
}{2023 -- 2024}\\[1pt]
\hspace*{12pt} Software Engineering Intern.
Synthetic data generation, benchmarking, and time-series synthesis conditioned on metadata.

\vspace{8pt}
\cvrow{%
  \textbf{Syntho B.V.} \hspace{4pt} Amsterdam, Netherlands%
}{2022 -- 2023}\\[1pt]
\hspace*{12pt} High School Intern.
Bias minimization and fairness in machine learning through synthetic data.

% ── Education ────────────────────────────────────────────────────────────────
\cvsection{Education}

\cvrow{%
  \textbf{MSc Computer Science} \hspace{4pt} Delft University of Technology%
}{2026 -- present}\\[2pt]
\hspace*{12pt}
Thesis: AI-agent supported migration of legacy systems at the Dutch Inspectorate for
Living Environment and Transport (ILT).\\
\hspace*{12pt}
Supervisor: Prof.\ Arie van Deursen.

\vspace{8pt}
\cvrow{%
  \textbf{Mathematics Minor} \hspace{4pt} University of Amsterdam%
}{2025 -- 2026}\\[2pt]
\hspace*{12pt}
Number and set theory, theory of statistics, differential equations, information theory,
and Markov chains.

\vspace{8pt}
\cvrow{%
  \textbf{BSc Computer Science and Engineering} \hspace{4pt} Delft University of Technology%
}{2023 -- 2026}\\[2pt]
\hspace*{12pt}
Data elective track.
Bachelor thesis: AST-guided membership inference for code language models
(published at FSE Companion 2026).

% ── Publications ─────────────────────────────────────────────────────────────
\cvsection{Publications}

\textit{Author ordering follows contribution. \textbf{Bold} indicates the presenting / corresponding author
where applicable. \underline{Underline} indicates Roham Koohestani.}

\vspace{6pt}
\textbf{Under Review}

\begin{publist}
\item[{[A2]}]
  \underline{Roham Koohestani}, Ziyou Li, Anton Podkopaev, Maliheh Izadi.
  \textit{Memory-Constrained Probabilistic Trace Models for Agentic AI.}
  Formal Aspects of Computing (FAC). \textit{Under review.}
  \href{https://arxiv.org/abs/2510.23487}{arXiv}

\item[{[A1]}]
  \underline{Roham Koohestani}, Ate\c{s} G\"{o}rpelio\u{g}lu, Egor Klimov,
  Burcu Kulahcioglu Ozkan, Maliheh Izadi.
  \textit{TriCEGAR: A Trace-Driven Abstraction Mechanism for Agentic AI.}
  Preprint; co-first author.
  \href{https://arxiv.org/abs/2601.22997}{arXiv} /
  \href{https://zenodo.org/records/18338703}{artifact}
\end{publist}

\vspace{6pt}
\textbf{Journal Publications}

\begin{publist}
\item[{[J1]}]
  \underline{Roham Koohestani}, Philippe de Bekker, Beg\"{u}m Ko\c{c}, Maliheh Izadi.
  \textit{Benchmarking AI Models in Software Engineering: A Review, Search Tool,
  and Enhancement Protocol.}
  IEEE Transactions on Software Engineering (TSE), 2025.
  Journal-first presentation at FSE 2026.
  \href{https://arxiv.org/abs/2503.05860}{arXiv} /
  \href{https://github.com/AISE-TUDelft/AI4SE-benchmarks}{code} /
  \href{https://evalpro.online/}{BenchScout}
\end{publist}

\vspace{6pt}
\textbf{Conference Publications}

\begin{publist}
\item[{[C5]}]
  \underline{Roham Koohestani}, Agnia Sergeyuk, David Gros, Claudio Spiess,
  Sergey Titov, Prem Devanbu, Maliheh Izadi.
  \textit{Does In-IDE Calibration of Large Language Models Work at Scale?}
  FSE Companion 2026, Industry Track. Co-first author.
  \href{https://doi.org/10.1145/3803437.3805234}{DOI} /
  \href{https://arxiv.org/abs/2510.22614}{arXiv}

\item[{[C4]}]
  \underline{Roham Koohestani}, Ali Al-Kaswan, Jonathan Katzy, Maliheh Izadi.
  \textit{AST-PAC: AST-guided Membership Inference for Code.}
  FSE Companion 2026, IVR Track. From bachelor thesis.
  \href{https://doi.org/10.1145/3803437.3805588}{DOI} /
  \href{https://doi.org/10.5281/zenodo.18348152}{artifact}

\item[{[C3]}]
  \underline{Roham Koohestani}, Parham Bateni, Aydin Ebrahimi, Behdad Etezadi,
  Kiarash Karimi, Maliheh Izadi.
  \textit{Code4Me V2: A Research-oriented Code-completion Platform.}
  ICSE Companion 2026, Demonstrations Track. Co-first author.
  \href{https://doi.org/10.1145/3774748.3787616}{DOI} /
  \href{https://arxiv.org/abs/2510.03755}{arXiv}

\item[{[C2]}]
  Amirhossein Deljouyi, \underline{Roham Koohestani}, Maliheh Izadi, Andy Zaidman.
  \textit{Leveraging Large Language Models for Enhancing the Understandability of
  Generated Unit Tests.}
  ICSE 2025.
  \href{https://arxiv.org/abs/2408.11710}{arXiv} /
  \href{https://github.com/amirdeljouyi/UTGen}{code}

\item[{[C1]}]
  \underline{Roham Koohestani}, Maliheh Izadi.
  \textit{HyperSeq: A Hyper-Adaptive Representation for Predictive Sequencing of States.}
  FSE Companion 2025.
  \href{https://doi.org/10.1145/3696630.3728526}{DOI} /
  \href{https://github.com/hyperseq-replication/package}{code}
\end{publist}

\vspace{6pt}
\textbf{Workshop Publications}

\begin{publist}
\item[{[W2]}]
  \underline{Roham Koohestani}.
  \textit{AgentGuard: Runtime Verification of AI Agents.}
  ASE 2025 Workshops (SE Agents). Sole author.
  \href{https://doi.org/10.1109/ASEW67777.2025.00023}{DOI} /
  \href{https://arxiv.org/abs/2509.23864}{arXiv}

\item[{[W1]}]
  \underline{Roham Koohestani}, Maliheh Izadi.
  \textit{Rethinking IDE Customization for Enhanced HAX: A Hyperdimensional Perspective.}
  IDE Workshop 2025 (co-located with ICSE).
  \href{https://doi.org/10.1109/IDE66625.2025.00007}{DOI}
\end{publist}

% ── Teaching ─────────────────────────────────────────────────────────────────
\cvsection{Teaching}

\cvrow{%
  \textbf{Teaching Assistant} \hspace{4pt} Delft University of Technology%
}{2024 -- 2026}\\[2pt]
\hspace*{12pt}
CS4570 Machine Learning for Software Engineering.\\[2pt]
\hspace*{12pt}
Supervised 50+ MSc students in research projects over two academic years, across
a 10-week intensive group-research course.
Coordinated assessment for a cohort of more than 130 students.

% ── Service ──────────────────────────────────────────────────────────────────
\cvsection{Service}

\textit{Co-Reviewing --- Conferences \& Journals}\\[2pt]
\hspace*{12pt} ICSE ('25, '26C1, '26C2), FSE ('25), ASE ('25), EMSE ('25), ISSTA ('26)

\vspace{6pt}
\textit{Reviewer --- Conference}\\[2pt]
\hspace*{12pt} ICSME Industry Track 2026

\vspace{6pt}
\textit{Reviewer --- Workshops}\\[2pt]
\hspace*{12pt} DeepLearning4Code Workshop @ NeurIPS 2025\\[1pt]
\hspace*{12pt} DeepLearning4Code Workshop @ ICML 2026\\[1pt]
\hspace*{12pt} FSE $\times$ AIWARE Competition --- Poisoned Chalice @ FSE 2026

\vspace{6pt}
\textit{Organizing}\\[2pt]
\hspace*{12pt} Web-Chair, AgenticSE Workshop @ ASE 2025

% ── End ──────────────────────────────────────────────────────────────────────
\end{document}
